---
title: "Comparison"
output: html_document
---
# Differences in countries vs. differences in COVID - 19

This section tries to answer the question whether countries with similar characteristics
experienced a similar course of pandemic in the selected period.




## COVID19 vs country characteristics 

In our approach we cluster countries based on how the pandemic evolved.
The evolution of pandemic is measured using the restrictions variables described in the
Introduction subsection [Variables].


### Dendrograms

```{r echo=FALSE,results='hide',fig.keep='all'}

data_ts_raw <- data
for(col in cols_cov){
  if(col!='stringency_index'){
    data_ts_raw[col] = data[col]/data$population
    }
}

data_ts <- data_ts_raw


for(measure_res in setdiff(cols_cov,c('population'))){


CharTraj <- data_ts[,c('id','date',measure_res)] %>% 
  replace(is.na(.), 0) %>% 
  pivot_wider(id_cols = id, names_from = 'date', values_from = measure_res) %>% 
  column_to_rownames()
  
hc <- invisible(tsclust(CharTraj, type = "hierarchical", 
              distance = "sbd", trace = TRUE,
              control = hierarchical_control(method = "average")))


hcd <- as.dendrogram(hc)
# Default plot
plot(hcd, type = "rectangle", axes = F, 
    main = paste0('Dendrogram for countries clustered by the measure:',measure_res)
    )

# make columns indicating clusters assignment
clusts <- cutree(hc,params$nclust)

clust_colname <- paste0(measure_res,'_cluster')
data[clust_colname] <- 1
data_ts[clust_colname] <- 1

for(cnt in names(clusts)){
data[data$id == cnt,clust_colname] <- clusts[cnt]
data_ts[data_ts$id == cnt,clust_colname] <- clusts[cnt]
  }

}


```

### Time series

```{r}
for(col in setdiff(cols_cov,c('population'))){
col_clust <- paste0(col,'_cluster')

data[,col_clust] <- as.factor(data[,col_clust])
data[col] <- fill(data[col],.direction = 'downup')

data %>% ggplot()+
  geom_line(aes_string(x='date',y=col,group = 'id',color = col_clust))+
  ggtitle(paste0('Cluster assignment based on ',col,' clustering.'))->p
print(p)
}
```

### Between cluster comparisons

After clustering we may visually examine if the groups are different in terms of socioeconomic factors.
 
```{r socio by clust, message=FALSE}

cluster_cols <- colnames(data)[grepl('cluster',colnames(data))]

for(col in cluster_cols){
  #col<-cluster_cols[1]
  df_plot <- data %>% group_by_at(vars(one_of(col))) %>% summarise(across(.cols = cols_soc,.funs = mean)) %>% unique()
  
  measure <- substring(col,1,nchar(col)-8)
  colnames(df_plot)[1] <- 'm'
  
  df_plot %>% 
    pivot_longer(cols = cols_soc) %>% 
    ggplot(aes(x = as.integer(m),y = value))+
    geom_bar(aes(fill=name), stat = 'identity', position = 'dodge')+
    scale_y_log10()+ 
    ylab('value on Log_10 scale')+
    xlab('cluster')+
    ggtitle(paste0('Means of WB indicators in clusters obtained by measure: ',measure)) +
    theme_classic() -> p 
  print(p)
  }

```

