---
title: "Introduction"
output: html_document
---
```{r source, include=FALSE}
source("../../R/dictionaries.R")
```

# Introduction

From Wikipedia:

>Coronavirus disease 2019 (COVID-19) is a contagious disease caused by severe 
acute respiratory syndrome coronavirus 2 (SARS-CoV-2). The first known case was
identified in Wuhan, China in December 2019. The disease has since spread worldwide,
leading to a pandemic.

This report aims to provide insight into the differences in the course of the pandemic in differences countries through simple and informative summaries and graphics.

## Data

### Countries and period

The report focuses on the following list of countries:
```{r countries used, results='asis'}
for (cnt in country_names) {
  cat(
    paste0('\n',
          '* ',
          '**',cnt,'**')
    )
}

```


in the period **`r params$start_date`** to **`r params$end_date`**. 

### Variables {.tabset}

Comparison between countries is made using a set of `r length(colnames(data)[-c(1:2)])`
characteristics. Their list and details can be found below.

#### List of variables used

```{r variables used, results = 'asis'}

for (cnt in colnames(data)[-c(1:2)]) {
  cat(
    paste0('\n',
          '* ',
          '**',cnt,'**')
    )
}

```

#### Details

```{r details of variables used, results = 'asis'}

for (col in colnames(data)[-c(1:2)]) {
  if(col  %in% c(cols_cov,cols_res)){
  cat(
    paste0('\n',
          '* ','**',col,'**',': ','*',dict_all[[col]],'*')
  )
  }else{
       cat(
    paste0('\n',
          '* ',
          '**',col,'**')
    )
    }
}
cat(paste0('\n\n',dict_all[['details_res']],' on restrictions variables.'))

```

### {-}

## Summary {.tabset}

Let us summarize the dataset:

* number of days analyzed: **`r data$date %>% unique() %>%  length() `**
* number of World Bank indicators used: **`r cols_soc %>%  length() `**
* number of pandemic measures used: **`r cols_soc %>%  length() `**
* number of restrictions measures used: **`r cols_soc %>% length() `**

Mean values of the characteristics:

### Table

```{r summary, results='asis'}
d <- data %>% 
  select(!c(2)) %>% #ditch date
  mutate(across(.cols = c(any_of(cols_cov),
                  -c(population)),
                .fns = list(per_100k_population = ~ .x/population*10000) ))%>% # get vars per 100k population
  group_by(id)  %>% # group by countries
  summarize(across(.cols=!cols_cov,
                   .fns = list(mean = ~ mean(.x, na.rm = TRUE)))) %>% 
  `colnames<-`(gsub('\\$','',colnames(.)))  # substitute special char $ to nothing
  
d %>%   knitr::kable(.,format = "html") %>% # table
  kableExtra::kable_paper() %>%
  kableExtra::scroll_box(width = "100%", height = "300px")

```


### Barplot
```{r barplot}
plot_df <- d %>% pivot_longer(-id) #%>%  filter(name != "GDP (current US)_mean")
plot_df %>% as.data.frame() %>% ggplot()+
  geom_bar(aes(fill = name,x = id,y = value ),stat = 'identity',position = 'dodge')+
  scale_y_log10()+ 
  ylab('value on Log_10 scale')+
  theme_classic()

```

