---
title: "Reactions"
output: html_document
---

# Countries' reactions

```{r first last country}
first <- data %>% 
  filter(date == min(data$date)) %>%  
  arrange(-confirmed) %>%  
  select(id) %>% 
  first() %>% 
  first() %>% 
  countrycode(origin = "iso3c", destination = 'country.name')

last <- data %>% 
  filter(date == min(data$date)) %>%  
  arrange(confirmed) %>%  
  select(id) %>% 
  first() %>% 
  first() %>% 
  countrycode(origin = "iso3c", destination = 'country.name')


```


`r first` was the country that experienced the highest number of total confirmed infections at
the beginning of the analyzed period, while `r last` had the fewest number of confirmed cases.

Let's examine how the countries reacted to pandemic in that time.

## Course of pandemic vs. measures enforced

The figures below depict how countries reacted to the pandemic.
The y-axis shows the intensity of restrictions indicated by various measures while
x-axis shows, depending on the variant, number of confirmed cases or the timeline.

### Stringency {.tabset}

Stringency measures the overall 'severity' of the lockdown policy.

Below we find graphs of stringency_index plotted against time and number of 
confirmed COVID-19 cases.

#### ...versus confirmed cases

```{r}

data %>%
  mutate(confirmed_per_100k_pop = confirmed/population*100000) %>% 
  replace(is.na(.), 0) %>% 
  select(id,date,confirmed_per_100k_pop,stringency_index) %>% 
  pivot_longer(-c(id,date,confirmed_per_100k_pop)) %>% 
  ggplot()+
  geom_line(aes(x=confirmed_per_100k_pop,y = value, color = id))+
  ggtitle("Stringency index")

```


#### ...in time

```{r}

data %>%
  mutate(confirmed_per_100k_pop = confirmed/population*100000) %>% 
  replace(is.na(.), 0) %>% 
  select(id,date,confirmed_per_100k_pop,stringency_index) %>% 
  pivot_longer(-c(id,date,confirmed_per_100k_pop)) %>% 
  ggplot()+
  geom_line(aes(x=date,y = value, color = id))+
  ggtitle("Stringency index")

```


### Other restrictions {.tabset}

Let us also analyze particular restrictive actions of the governments.

#### ...versus confirmed cases

```{r}
other_measures <- setdiff(cols_res,c('stringency_index'))

for(cnt in unique(data$id)){
data %>%
  filter(id == cnt) %>% 
  mutate(confirmed_per_100k_pop = confirmed/population*100000) %>% 
  replace(is.na(.), 0) %>% 
  select(id,date,confirmed_per_100k_pop,other_measures) %>% 
  pivot_longer(-c(id,date,confirmed_per_100k_pop)) %>% 
  ggplot()+
  geom_line(aes(x=confirmed_per_100k_pop, color = name ,y = value))+
    ggtitle(countrycode(cnt,'iso3c','country.name')) -> plot
  print(plot)}
```

#### ...in time

```{r}


for(cnt in unique(data$id)){
data %>%
  filter(id == cnt) %>% 
  mutate(confirmed_per_100k_pop = confirmed/population*100000) %>% 
  replace(is.na(.), 0) %>% 
  select(id,date,confirmed_per_100k_pop,other_measures) %>% 
  pivot_longer(-c(id,date,confirmed_per_100k_pop)) %>% 
  ggplot()+
  geom_line(aes(x=date, color = name ,y = value))+
    ggtitle(countrycode(cnt,'iso3c','country.name'))-> plot
  print(plot)}
```

