---
title: "Vaccines"
output: html_document
---

# Vaccinations {.tabset}


```{r}
min_dates <- data %>% 
  filter(!is.na(vaccines)) %>%
  group_by(id) %>%
  summarise(min_date = min(date)) 

tot_vacc <- data %>% 
  fill(vaccines, .direction = 'downup') %>% 
  group_by(id) %>% 
  summarise(vaccine = last(vaccines))

```


The vaccination process started in **`r min(min_dates$min_date)`** and in the whole period
a total number of doses administered in all selected countries amounted to **`r sum(tot_vacc$vaccine)`**.

In the graphs below we can see the cumulative number of doses administered and
number of doses administered per 100k population. It is crucial to mention that 
the latter value is not number of people vaccinated (only a proxy of it), as some 
vaccines require multiple doses for full efficiency. 

## Number of doses

```{r}

data %>% 
  filter(!is.na(vaccines)) %>% 
  fill(vaccines, .direction = 'downup') %>% 
  ggplot()+
  geom_line(aes(x=date,y=vaccines,color = id ))+
  ylab('cumulative doses of vaccine')+
  theme_bw()

```

## Number of doses per population

```{r}

data %>% 
  filter(!is.na(vaccines)) %>% 
  fill(vaccines, .direction = 'downup') %>% 
  mutate(vaccines = vaccines/population*100000) %>% 
  ggplot()+
  geom_line(aes(x=date,y=vaccines,color = id ))+
  ylab('cumulative doses of vaccine per 100k population')+
  theme_bw()

```
